Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-03-08 Paper/paper.tex
Update

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\usepackage{color}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, the yellow
    curves show the best-fit double power law luminosity function in
    that redshift bin.  The green curves show the posterior
    distribution of the global model.  The global model agrees very
    well with the data in all redshift bins, except those spanned by
    BOSS, as BOSS quasars are excluded from the global analysis.}
  \label{fig:mosaic_global}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[scale=0.65]{g.pdf}
  \end{center}
  \caption{AGN contribution to the hydrogen photoionisation rate,
    assuming 100\% escape fraction.  Model luminosity functions are
    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
    the right panel.  The solid black curve shows the hydrogen
    photoionisate rate in our best-fit global model, and the yellow
    curves show a random sample from the global posterior.  The red
    points with error bars in this figure show the measurements of
    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
    forest, and the orange points show the measurements by
    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
    dashed green curve shows the hydrogen photoionisation rate
    evolution in the model of \citet{2012ApJ...746..125H}, while the
    solid green curve shows the contribution of quasars to it. \gk{Two
      problems to be addressed in these plots: (a) there is a
      contribution of $z>7$ qsos to the photoionisation rate at $z<7$
      but because our emissivity diverges at $z>7$, I had a to put an
      arbitrary cut-off; (b) the plots are too messy; we probably
      should show fewer things.}}
  \label{fig:gammapi}
\end{figure*}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
  \end{center}
  \caption{Photon underproduction crisis.\label{fig:puc}}
\end{figure}

@@

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
  \end{center}
  \caption{Helium reionization.}
\end{figure}

@@

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\usepackage{color}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\usepackage{supertabular}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
    % mosaic.py 
  \end{center}
  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.
    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
    binned luminosity functions.  In each redshift bin, the yellow
    curves show the best-fit double power law luminosity function in
    that redshift bin.  The green curves show the posterior
    distribution of the global model.  The global model agrees very
    well with the data in all redshift bins, except those spanned by
    BOSS, as BOSS quasars are excluded from the global
    analysis. \gk{Show all three models here.}}
  \label{fig:mosaic_global}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    % rtg2.draw_g_paper() 
    \includegraphics[scale=0.65]{g.pdf}
  \end{center}
  \caption{AGN contribution to the hydrogen photoionisation rate,
    assuming 100\% escape fraction.  Model luminosity functions are
    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
    the right panel.  The solid black curve shows the hydrogen
    photoionisate rate in our best-fit global model, and the yellow
    curves show a random sample from the global posterior.  The red
    points with error bars in this figure show the measurements of
    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
    forest, and the orange points show the measurements by
    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
    dashed green curve shows the hydrogen photoionisation rate
    evolution in the model of \citet{2012ApJ...746..125H}, while the
    solid green curve shows the contribution of quasars to it. }
  \label{fig:gammapi}
\end{figure*}

@@

@@

\begin{figure}
  \begin{center}
    % rtg2.draw_g_puc()
    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
  \end{center}
  \caption{Evolution of the hydrogen photoionisation rate at low
    redshifts (cf.\ Figure~\ref{fig:gammapi}).\label{fig:puc}}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
  \end{center}
  \caption{Helium reionization. \gk{What is La Plante's luminosity
      limit?  Why is his redshift of reionization lower than ours?
      Waiting for Puchwein to give us his model.  Do we need a table
      for Q evolution of H and He?  Should we tabulate Helium
      photoionisation rate?}}
\end{figure}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_g.pdf}
  \end{center}
  \caption{Effect of including Giallongo qsos in our analysis.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{giallongo_compare.pdf}
  \end{center}
  \caption{Comparison of our LFs with Giallongo's LFs.}
\end{figure*}

\section{Table of emissivities}
\label{sec:tables}

Table~\ref{tab:gamma} shows the LyC emissivities and the resultant
hydrogen photoionisation rate due to quasars down to magnitudes
$M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the curves
shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
photoionisation rate calculation assumes an HI column density given by
\citet{2012ApJ...746..125H}.  See Sections XX and XX for further
details.

\begin{table*}
  \caption{LyC emissivities and the resultant hydrogen photoionisation
    rate due to quasars down to magnitudes $M_{1450}=-18$ and
    $M_{1450}=-21$.  These numbers describe the curves shown in
    Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The photoionisation
    rate calculation assumes an HI column density given by
    \citet{2012ApJ...746..125H}.  See Sections XX and XX for further
    details.  \gk{Do we need another table for the emissivities from
      individual models?}}
  \label{tab:gamma}
  \begin{tabular}{ccccc}
    \hline
    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
    \hline
    0.0 & 5.090e--14 & 2.822e--14 & 1.383e+23 & 7.011e+22 \\
    0.1 & 7.036e--14 & 4.069e--14 & 2.231e+23 & 1.176e+23 \\
    0.2 & 9.461e--14 & 5.690e--14 & 3.419e+23 & 1.877e+23 \\
    0.3 & 1.248e--13 & 7.787e--14 & 5.019e+23 & 2.873e+23 \\
    0.4 & 1.614e--13 & 1.041e--13 & 7.098e+23 & 4.240e+23 \\
    0.5 & 2.051e--13 & 1.363e--13 & 9.717e+23 & 6.056e+23 \\
    0.6 & 2.566e--13 & 1.750e--13 & 1.293e+24 & 8.401e+23 \\
    0.7 & 3.164e--13 & 2.208e--13 & 1.676e+24 & 1.135e+24 \\
    0.8 & 3.845e--13 & 2.736e--13 & 2.124e+24 & 1.495e+24 \\
    0.9 & 4.605e--13 & 3.330e--13 & 2.636e+24 & 1.923e+24 \\
    1.0 & 5.433e--13 & 3.980e--13 & 3.208e+24 & 2.419e+24 \\
    1.1 & 6.309e--13 & 4.667e--13 & 3.835e+24 & 2.978e+24 \\
    1.2 & 7.207e--13 & 5.367e--13 & 4.507e+24 & 3.589e+24 \\
    1.3 & 8.092e--13 & 6.046e--13 & 5.216e+24 & 4.237e+24 \\
    1.4 & 8.931e--13 & 6.675e--13 & 5.946e+24 & 4.902e+24 \\
    1.5 & 9.715e--13 & 7.246e--13 & 6.684e+24 & 5.559e+24 \\
    1.6 & 1.037e--12 & 7.693e--13 & 7.414e+24 & 6.185e+24 \\
    1.7 & 1.087e--12 & 8.003e--13 & 8.117e+24 & 6.754e+24 \\
    1.8 & 1.131e--12 & 8.246e--13 & 8.779e+24 & 7.245e+24 \\
    1.9 & 1.163e--12 & 8.364e--13 & 9.384e+24 & 7.642e+24 \\
    2.0 & 1.183e--12 & 8.386e--13 & 9.917e+24 & 7.932e+24 \\
    2.1 & 1.195e--12 & 8.322e--13 & 1.037e+25 & 8.112e+24 \\
    2.2 & 1.194e--12 & 8.156e--13 & 1.073e+25 & 8.184e+24 \\
    2.3 & 1.187e--12 & 7.941e--13 & 1.099e+25 & 8.153e+24 \\
    2.4 & 1.168e--12 & 7.636e--13 & 1.115e+25 & 8.030e+24 \\
    2.5 & 1.145e--12 & 7.308e--13 & 1.121e+25 & 7.827e+24 \\
    2.6 & 1.112e--12 & 6.915e--13 & 1.118e+25 & 7.558e+24 \\
    2.7 & 1.075e--12 & 6.516e--13 & 1.105e+25 & 7.237e+24 \\
    2.8 & 1.031e--12 & 6.080e--13 & 1.085e+25 & 6.877e+24 \\
    2.9 & 9.835e--13 & 5.648e--13 & 1.057e+25 & 6.490e+24 \\
    3.0 & 9.319e--13 & 5.207e--13 & 1.022e+25 & 6.087e+24 \\
    3.1 & 8.780e--13 & 4.774e--13 & 9.824e+24 & 5.676e+24 \\
    3.2 & 8.227e--13 & 4.354e--13 & 9.385e+24 & 5.267e+24 \\
    3.3 & 7.658e--13 & 3.945e--13 & 8.914e+24 & 4.864e+24 \\
    3.4 & 7.102e--13 & 3.565e--13 & 8.422e+24 & 4.473e+24 \\
    3.5 & 6.545e--13 & 3.202e--13 & 7.916e+24 & 4.098e+24 \\
    3.6 & 6.006e--13 & 2.865e--13 & 7.406e+24 & 3.740e+24 \\
    3.7 & 5.487e--13 & 2.554e--13 & 6.898e+24 & 3.402e+24 \\
    3.8 & 4.988e--13 & 2.265e--13 & 6.399e+24 & 3.085e+24 \\
    3.9 & 4.521e--13 & 2.006e--13 & 5.912e+24 & 2.789e+24 \\
    4.0 & 4.082e--13 & 1.769e--13 & 5.443e+24 & 2.515e+24 \\
    4.1 & 3.671e--13 & 1.554e--13 & 4.993e+24 & 2.262e+24 \\
    4.2 & 3.295e--13 & 1.363e--13 & 4.566e+24 & 2.029e+24 \\
    4.3 & 2.948e--13 & 1.192e--13 & 4.163e+24 & 1.816e+24 \\
    4.4 & 2.630e--13 & 1.039e--13 & 3.784e+24 & 1.622e+24 \\
    4.5 & 2.342e--13 & 9.045e--14 & 3.431e+24 & 1.445e+24 \\
    4.6 & 2.081e--13 & 7.854e--14 & 3.102e+24 & 1.286e+24 \\
    4.7 & 1.845e--13 & 6.803e--14 & 2.798e+24 & 1.141e+24 \\
    4.8 & 1.633e--13 & 5.883e--14 & 2.518e+24 & 1.011e+24 \\
    4.9 & 1.444e--13 & 5.078e--14 & 2.262e+24 & 8.944e+23 \\
    5.0 & 1.274e--13 & 4.373e--14 & 2.027e+24 & 7.898e+23 \\
    \hline
  \end{tabular}
\end{table*}

\begin{table*}
  \contcaption{LyC emissivities and the resultant hydrogen
    photoionisation rate due to quasars down to magnitudes
    $M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the
    curves shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
    photoionisation rate calculation assumes an HI column density
    given by \citet{2012ApJ...746..125H}.  See Sections XX and XX for
    further details.}
  \label{tab:gamma}
  \begin{tabular}{ccccc}
    \hline
    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
    \hline
    5.1 & 1.121e--13 & 3.758e--14 & 1.813e+24 & 6.963e+23 \\
    5.2 & 9.851e--14 & 3.222e--14 & 1.618e+24 & 6.129e+23 \\
    5.3 & 8.622e--14 & 2.752e--14 & 1.442e+24 & 5.387e+23 \\
    5.4 & 7.497e--14 & 2.333e--14 & 1.283e+24 & 4.728e+23 \\
    5.5 & 6.433e--14 & 1.952e--14 & 1.139e+24 & 4.143e+23 \\
    5.6 & 5.346e--14 & 1.579e--14 & 1.010e+24 & 3.626e+23 \\
    5.7 & 4.420e--14 & 1.269e--14 & 8.942e+23 & 3.169e+23 \\
    5.8 & 3.635e--14 & 1.014e--14 & 7.905e+23 & 2.766e+23 \\
    5.9 & 2.971e--14 & 8.054e--15 & 6.978e+23 & 2.412e+23 \\
    6.0 & 2.415e--14 & 6.354e--15 & 6.152e+23 & 2.100e+23 \\
    6.1 & 1.952e--14 & 4.982e--15 & 5.416e+23 & 1.826e+23 \\
    6.2 & 1.570e--14 & 3.883e--15 & 4.762e+23 & 1.587e+23 \\
    6.3 & 1.255e--14 & 3.004e--15 & 4.182e+23 & 1.377e+23 \\
    6.4 & 9.968e--15 & 2.310e--15 & 3.668e+23 & 1.193e+23 \\
    6.5 & 7.880e--15 & 1.766e--15 & 3.214e+23 & 1.033e+23 \\
    6.6 & 6.200e--15 & 1.343e--15 & 2.813e+23 & 8.940e+22 \\
    6.7 & 4.853e--15 & 1.015e--15 & 2.459e+23 & 7.726e+22 \\
    6.8 & 3.781e--15 & 7.634e--16 & 2.148e+23 & 6.670e+22 \\
    6.9 & 2.936e--15 & 5.721e--16 & 1.874e+23 & 5.753e+22 \\
    7.0 & 2.275e--15 & 4.277e--16 & 1.633e+23 & 4.958e+22 \\
    7.1 & 1.760e--15 & 3.192e--16 & 1.422e+23 & 4.269e+22 \\
    7.2 & 1.360e--15 & 2.379e--16 & 1.237e+23 & 3.672e+22 \\
    7.3 & 1.052e--15 & 1.775e--16 & 1.075e+23 & 3.156e+22 \\
    7.4 & 8.149e--16 & 1.327e--16 & 9.336e+22 & 2.710e+22 \\
    7.5 & 6.325e--16 & 9.947e--17 & 8.100e+22 & 2.326e+22 \\
    7.6 & 4.920e--16 & 7.477e--17 & 7.021e+22 & 1.994e+22 \\
    7.7 & 3.843e--16 & 5.645e--17 & 6.082e+22 & 1.709e+22 \\
    7.8 & 3.010e--16 & 4.278e--17 & 5.263e+22 & 1.463e+22 \\
    7.9 & 2.365e--16 & 3.253e--17 & 4.552e+22 & 1.251e+22 \\
    8.0 & 1.864e--16 & 2.483e--17 & 3.933e+22 & 1.070e+22 \\
    8.1 & 1.473e--16 & 1.902e--17 & 3.396e+22 & 9.138e+21 \\
    8.2 & 1.169e--16 & 1.462e--17 & 2.930e+22 & 7.800e+21 \\
    8.3 & 9.297e--17 & 1.128e--17 & 2.527e+22 & 6.654e+21 \\
    8.4 & 7.413e--17 & 8.725e--18 & 2.177e+22 & 5.673e+21 \\
    8.5 & 5.924e--17 & 6.767e--18 & 1.874e+22 & 4.833e+21 \\
    8.6 & 4.744e--17 & 5.260e--18 & 1.613e+22 & 4.115e+21 \\
    8.7 & 3.809e--17 & 4.100e--18 & 1.387e+22 & 3.502e+21 \\
    8.8 & 3.066e--17 & 3.205e--18 & 1.192e+22 & 2.978e+21 \\
    8.9 & 2.472e--17 & 2.510e--18 & 1.024e+22 & 2.531e+21 \\
    9.0 & 1.996e--17 & 1.969e--18 & 8.785e+21 & 2.149e+21 \\
    9.1 & 1.614e--17 & 1.547e--18 & 7.536e+21 & 1.825e+21 \\
    9.2 & 1.308e--17 & 1.218e--18 & 6.460e+21 & 1.548e+21 \\
    9.3 & 1.061e--17 & 9.604e--19 & 5.535e+21 & 1.313e+21 \\
    9.4 & 8.628e--18 & 7.588e--19 & 4.739e+21 & 1.112e+21 \\
    9.5 & 7.022e--18 & 6.002e--19 & 4.056e+21 & 9.423e+20 \\
    9.6 & 5.722e--18 & 4.753e--19 & 3.469e+21 & 7.978e+20 \\
    9.7 & 4.667e--18 & 3.769e--19 & 2.966e+21 & 6.751e+20 \\
    9.8 & 3.810e--18 & 2.991e--19 & 2.534e+21 & 5.709e+20 \\
    9.9 & 3.116e--18 & 2.377e--19 & 2.164e+21 & 4.826e+20 \\
    10.0 & 2.551e--18 & 1.892e--19 & 1.847e+21 & 4.078e+20 \\
    \hline
  \end{tabular}
\end{table*}

\begin{table*}
  \contcaption{LyC emissivities and the resultant hydrogen
    photoionisation rate due to quasars down to magnitudes
    $M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the
    curves shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
    photoionisation rate calculation assumes an HI column density
    given by \citet{2012ApJ...746..125H}.  See Sections XX and XX for
    further details.}
  \label{tab:gamma}
  \begin{tabular}{ccccc}
    \hline
    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
    \hline
    10.1 & 2.091e--18 & 1.507e--19 & 1.576e+21 & 3.444e+20 \\
    10.2 & 1.715e--18 & 1.201e--19 & 1.344e+21 & 2.907e+20 \\
    10.3 & 1.407e--18 & 9.584e--20 & 1.145e+21 & 2.453e+20 \\
    10.4 & 1.156e--18 & 7.650e--20 & 9.756e+20 & 2.069e+20 \\
    10.5 & 9.500e--19 & 6.112e--20 & 8.307e+20 & 1.744e+20 \\
    10.6 & 7.820e--19 & 4.890e--20 & 7.071e+20 & 1.470e+20 \\
    10.7 & 6.441e--19 & 3.915e--20 & 6.015e+20 & 1.238e+20 \\
    10.8 & 5.309e--19 & 3.136e--20 & 5.115e+20 & 1.042e+20 \\
    10.9 & 4.377e--19 & 2.513e--20 & 4.348e+20 & 8.771e+19 \\
    11.0 & 3.611e--19 & 2.015e--20 & 3.694e+20 & 7.378e+19 \\
    11.1 & 2.980e--19 & 1.616e--20 & 3.137e+20 & 6.204e+19 \\
    11.2 & 2.462e--19 & 1.297e--20 & 2.664e+20 & 5.215e+19 \\
    11.3 & 2.036e--19 & 1.042e--20 & 2.260e+20 & 4.382e+19 \\
    11.4 & 1.685e--19 & 8.378e--21 & 1.917e+20 & 3.681e+19 \\
    11.5 & 1.394e--19 & 6.737e--21 & 1.626e+20 & 3.091e+19 \\
    11.6 & 1.154e--19 & 5.419e--21 & 1.378e+20 & 2.594e+19 \\
    11.7 & 9.559e--20 & 4.360e--21 & 1.168e+20 & 2.176e+19 \\
    11.8 & 7.919e--20 & 3.509e--21 & 9.889e+19 & 1.825e+19 \\
    11.9 & 6.564e--20 & 2.826e--21 & 8.372e+19 & 1.530e+19 \\
    12.0 & 5.447e--20 & 2.278e--21 & 7.086e+19 & 1.283e+19 \\
    12.1 & 4.521e--20 & 1.836e--21 & 5.995e+19 & 1.075e+19 \\
    12.2 & 3.754e--20 & 1.481e--21 & 5.070e+19 & 9.002e+18 \\
    12.3 & 3.117e--20 & 1.195e--21 & 4.287e+19 & 7.537e+18 \\
    12.4 & 2.589e--20 & 9.637e--22 & 3.623e+19 & 6.309e+18 \\
    12.5 & 2.151e--20 & 7.776e--22 & 3.061e+19 & 5.279e+18 \\
    12.6 & 1.788e--20 & 6.275e--22 & 2.586e+19 & 4.416e+18 \\
    12.7 & 1.487e--20 & 5.068e--22 & 2.183e+19 & 3.693e+18 \\
    12.8 & 1.237e--20 & 4.095e--22 & 1.843e+19 & 3.087e+18 \\
    12.9 & 1.029e--20 & 3.309e--22 & 1.555e+19 & 2.580e+18 \\
    13.0 & 8.567e--21 & 2.674e--22 & 1.312e+19 & 2.156e+18 \\
    13.1 & 7.131e--21 & 2.162e--22 & 1.106e+19 & 1.801e+18 \\
    13.2 & 5.935e--21 & 1.747e--22 & 9.325e+18 & 1.503e+18 \\
    13.3 & 4.940e--21 & 1.412e--22 & 7.859e+18 & 1.255e+18 \\
    13.4 & 4.112e--21 & 1.141e--22 & 6.621e+18 & 1.047e+18 \\
    13.5 & 3.424e--21 & 9.229e--23 & 5.577e+18 & 8.739e+17 \\
    13.6 & 2.851e--21 & 7.465e--23 & 4.696e+18 & 7.289e+17 \\
    13.7 & 2.374e--21 & 6.036e--23 & 3.953e+18 & 6.078e+17 \\
    13.8 & 1.975e--21 & 4.879e--23 & 3.327e+18 & 5.067e+17 \\
    13.9 & 1.643e--21 & 3.942e--23 & 2.799e+18 & 4.223e+17 \\
    14.0 & 1.365e--21 & 3.182e--23 & 2.354e+18 & 3.518e+17 \\
    14.1 & 1.133e--21 & 2.566e--23 & 1.980e+18 & 2.931e+17 \\
    14.2 & 9.381e--22 & 2.066e--23 & 1.664e+18 & 2.441e+17 \\
    14.3 & 7.750e--22 & 1.659e--23 & 1.399e+18 & 2.032e+17 \\
    14.4 & 6.384e--22 & 1.330e--23 & 1.175e+18 & 1.691e+17 \\
    14.5 & 5.229e--22 & 1.060e--23 & 9.873e+17 & 1.408e+17 \\
    14.6 & 4.245e--22 & 8.375e--24 & 8.292e+17 & 1.171e+17 \\
    14.7 & 3.395e--22 & 6.526e--24 & 6.962e+17 & 9.741e+16 \\
    14.8 & 2.641e--22 & 4.951e--24 & 5.844e+17 & 8.100e+16 \\
    14.9 & 1.935e--22 & 3.542e--24 & 4.904e+17 & 6.735e+16 \\
    15.0 & 1.182e--22 & 2.116e--24 & 4.115e+17 & 5.598e+16 \\
    \hline
  \end{tabular}
\end{table*}

\section{Code and data}

We make the homogenised quasar data and the code developing and
analysing luminosity function models available at
\url{https://github.com/gkulkarni/QLF} under the MIT open source
software license.  \gk{Remember to make URL public and set appropriate
  license upon publication of paper.}
